\section*{Question}
\textit{(On the next page there is a table.)} Next to your name you can find five numbers under the column $G \left( X, X' \right)$. Give the contribution of those graphs to $G \left( X, X' \right)$ in coordinate space. Choose appropriate coordinates at the vertices and write it on your figures in the solutions. Next to your name you can find another five numbers under the column $G \left( \boldsymbol{k}, i \omega_{n} \right)$. Give the contribution of those graphs to $G \left( \boldsymbol{k}, i \omega_{n} \right)$. Once again, use clear notations for your conventions together with a picture showing the newly introduced momenta and frequencies. Classify your graphs if they are reducible or irreducible. \\ \\
The row of the table with my name:
\begin{center}
\begin{tabular}{|r|c|c|c|c|c|c||c|c|c|c|c|}
\hline
No.    & Name       & \multicolumn{5}{c||}{$G \left( X, X' \right)$} & \multicolumn{5}{c|}{$G \left( \boldsymbol{k}, i \omega_{n} \right)$} \\
\hline
\vdots & \vdots     & \multicolumn{5}{c||}{\vdots}                   & \multicolumn{5}{c|}{\vdots}        \\
\hline
17     & Pál Balázs &  8  &  5  &  6  &  10  &  3                    &  7  &  2  &  4  &  1  &  9         \\
\hline
\vdots & \vdots     & \multicolumn{5}{c||}{\vdots}                   & \multicolumn{5}{c|}{\vdots}        \\
\hline
\end{tabular}
\end{center}

\section*{Reducibility}

\textbf{Def.}\ \ \ We call a diagram \textbf{reducible} which fall into two disjunct pieces if we cut one internal propagator line. \\
\textbf{Def.}\ \ \ Similarly, we call a diagram \textbf{irreducible} which does not fall into two disjunct pieces if we cut one internal propagator line. \\ \\
Using these definitions, we can easily identify the reducible and irreducible graphs:

\begin{center}
\begin{tabular}{|c|c|c|c||c|c|c|c|c|c|}
\hline
\multicolumn{4}{|c||}{Reducible graphs} & \multicolumn{6}{c|}{Irreducible graphs} \\
\hline
1 & 3 & 7 & 8 & 2 & 4 & 5 & 6 & 9 & 10                                            \\
\hline
\end{tabular}
\end{center}

\section*{Expressing the graphs}

\input{text_src/graph1.tex}
\input{text_src/graph2.tex}
\input{text_src/graph3.tex}
\input{text_src/graph4.tex}
\input{text_src/graph5.tex}
\input{text_src/graph6.tex}
\input{text_src/graph7.tex}
\input{text_src/graph8.tex}
\input{text_src/graph9.tex}
\input{text_src/graph10.tex}